\section*{\centering\heiti\zihao{4}参考文献}
\addcontentsline{toc}{section}{参考文献}
\begin{thebibliography}{99}

\bibitem{flink}
Apache Software Foundation.
\textit{Apache Flink Documentation}.
https://nightlies.apache.org/flink/

\bibitem{kafka}
Apache Software Foundation.
\textit{Apache Kafka Documentation}.
https://kafka.apache.org/documentation/

\bibitem{redis}
Redis Ltd.
\textit{Redis Documentation}.
https://redis.io/docs/

\bibitem{fastapi}
FastAPI.
\textit{FastAPI Documentation}.
https://fastapi.tiangolo.com/

\bibitem{lightgbm}
Ke, G., Meng, Q., Finley, T., Wang, T., Chen, W., Ma, W., Ye, Q., \& Liu, T.-Y. (2017).
LightGBM: A highly efficient gradient boosting decision tree.
\textit{Advances in Neural Information Processing Systems}, 30.

\bibitem{xgboost}
Chen, T., \& Guestrin, C. (2016).
XGBoost: A scalable tree boosting system.
\textit{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, 785--794.

\bibitem{catboost}
Prokhorenkova, L., Gusev, G., Vorobev, A., Dorogush, A. V., \& Gulin, A. (2018).
CatBoost: unbiased boosting with categorical features.
\textit{Advances in Neural Information Processing Systems}, 31.

\bibitem{graphsage}
Hamilton, W. L., Ying, R., \& Leskovec, J. (2017).
Inductive representation learning on large graphs.
\textit{Advances in Neural Information Processing Systems}, 30.

\bibitem{auc}
Davis, J., \& Goadrich, M. (2006).
The relationship between Precision-Recall and ROC curves.
\textit{Proceedings of the 23rd International Conference on Machine Learning}, 233--240.

\bibitem{paysim}
Lopez-Rojas, E. A., Elmir, A., \& Axelsson, S. (2016).
PaySim: A financial mobile money simulator for fraud detection.
\textit{Proceedings of the 28th European Modeling and Simulation Symposium}.

\bibitem{banksim}
Lopez-Rojas, E. A., \& Axelsson, S. (2014).
BankSim: A bank payments simulator for fraud detection research.
\textit{Proceedings of the 26th European Modeling and Simulation Symposium}.

\bibitem{ieeecis}
IEEE Computational Intelligence Society.
\textit{IEEE-CIS Fraud Detection}.
Kaggle Competition, 2019.

\bibitem{creditcard}
Dal Pozzolo, A., Caelen, O., Johnson, R. A., \& Bontempi, G. (2015).
Calibrating probability with undersampling for unbalanced classification.
\textit{2015 IEEE Symposium Series on Computational Intelligence}, 159--166.

\bibitem{elliptic}
Weber, M., Domeniconi, G., Chen, J., Weidele, D. K. I., Bellei, C., Robinson, T., \& Leiserson, C. E. (2019).
Anti-money laundering in Bitcoin: Experimenting with graph convolutional networks for financial forensics.
\textit{KDD Workshop on Anomaly Detection in Finance}.

\bibitem{dgraphfin}
Huang, X., et al. (2022).
DGraph: A large-scale financial dataset for graph anomaly detection.
\textit{Advances in Neural Information Processing Systems}, 35.

\bibitem{samld}
Oztas, B., et al. (2023).
SAML-D: Synthetic anti-money laundering transaction data.
\textit{Data in Brief}, 47.

\bibitem{amlsim}
IBM Research.
\textit{AMLSim: Anti-Money Laundering Simulator}.
https://github.com/IBM/AMLSim

\bibitem{docker}
Docker Inc.
\textit{Docker Compose Documentation}.
https://docs.docker.com/compose/

\end{thebibliography}
